Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-02-01 vesicle_code/docs/adhesion/adhesion.tex
worked on extensional

We further characterize the dynamics by examining the vorticity and
total force on the vesicles.

>>>>

We further characterize the rotating dynamics of a doublet by examining
the vorticity and total force on the vesicles.  In Figure~\ref{}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[width = 0.19\textwidth,trim={3cm 0cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[width = 0.19\textwidth,trim={6cm 0cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[width = 0.19\textwidth,trim={3cm 0cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
%  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
%  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
%  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
%  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
%  \caption{\label{fig:extensionalVorticity} Stuff here}
\end{figure}
